---
title: FinishINK WWX 
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
    theme: flatly
    #runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(highcharter)
library(tidyverse)
library(maps)
library(htmlwidgets)
library(leaflet)
library(lubridate)
library(echarts4r)
library(dplyr)
library(DT)
library(mapview)
library(sf)
library(sp)
library(janitor)
library(scales)
library(gtsummary)
library(tmap)
```


# {General Number of Systems & Doors}
```{r}
  
```


```{r read}

Data <- read_csv("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Combined Files/Data.csv")

County_shp<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Water Infrastructure/Administrative Boundary/Nakuru County Boundary.shp")

SubCounties_shp <-read_sf("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Sub_Counties.shp")

Interested_SubCounties <- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Interested.shp")

Toilets2021<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/Data2021.shp")

Toilets2022<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/Data2022.shp")

Toilets2023<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/Data2023.shp")

WWX_Previous_Toilets<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/1K_WWX_Toilets.shp")
 
NCSP_Toilets<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/NCSP_Toilets.shp")

Datashp<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/Datashp.shp")

Nawasscoshp<- read_sf ("E:/Nakuru WaterWax/Vei project/PostgressSQL Database/Sanitation/Constructed and Improved Toilets under Partnaship/Boundaries/Toilets/Nawasscoshp.shp")



```

Row {data-width=500}
-----------------------------------------------------------------------

### Number of systems Per Sub-County

```{r}

Data %>% 
  group_by(Sub_county)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'bar', hcaes(Sub_county, Number), color='green',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>%
  hc_title(
    text='System in Nakuru Per Sub-Counties',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_caption(text="Points generated from coordinates") %>% 
  hc_add_theme(hc_theme_flat())%>% 
  #hc_add_theme(hc_theme_hcrt()) %>% 
  hc_yAxis(title=list(text='Number of System' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))
  

```

Row {data-width=500}
-----------------------------------------------------------------------

### Number of Toilets Per Sub-County

```{r}

Data %>% 
  group_by(Sub_county)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
  arrange(System_Doors)%>%# indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Sub_county, y= System_Doors), color='magenta',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nakuru System Doors per Sub-County ',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_flat())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))
```


Row {data-width=500}
-----------------------------------------------------------------------

### Number of Systems Per Year

```{r}

Data %>% 
  group_by(Year)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=Number),  color='pink',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nakuru Number of Systems per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Systems' )) %>% 
  hc_xAxis(title=list(text='Years'))



```



Row {data-width=500}
-----------------------------------------------------------------------

### Number of Toilets Per Year

```{r}

Data %>% 
  group_by(Year)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
 #arrange(System_Doors) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=System_Doors),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nakuru Number of Systems Doors per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Systems' )) %>% 
  hc_xAxis(title=list(text='Years'))
```



# {General Map}
```{r}
  
```

Row {data-height=400}
-----------------------------------------------------------------------

### General map of the Systems

```{r}

```



```{r}
leaflet() %>%
  

#addProviderTiles('Esri.WorldImegary') %>% 
  setView(lng = 36.058758, lat= -0.427551, zoom=9) %>%
 addScaleBar(position='bottomleft') %>% 
  addMeasure() %>%
  addCircles(data = Toilets2021, color = 'green', opacity = 0.4) %>% 
  addCircles(data = Toilets2022, color = 'yellow', opacity = 0.4) %>% 
  addCircles(data = Toilets2023, color = 'blue', opacity = 0.4) %>% 
  addCircles(data = NCSP_Toilets, color = 'black', opacity = 0.4) %>% 
  addCircles(data = WWX_Previous_Toilets, color = 'grey', opacity = 0.5) %>% 
  addPolygons(data = SubCounties_shp, opacity = 0.1, fillColor = 'n') %>% 
  addPolygons(data= Interested_SubCounties, color = 'red', weight = 3, opacity = 0.2) %>%
  
  addLayersControl(overlayGroups = c('SubCounties_shp','Interested_SubCounties','Toilets2021',          'Toilets2022', 'Toilets2023'),
                   baseGroups = 'CartoDB.Voyager', options=layersControlOptions(collapsed=FALSE)) %>% 
  #addLegend(position = 'bottomright', pal = F, values = T) %>% 
  addProviderTiles("CartoDB.Voyager") 
```

# {Monthly Entries Trend}
```{r}
  
```




Row {data-height=400}
-----------------------------------------------------------------------

### Number of entries, Year 2021
```{r}
Data2021<-Data %>% 
   dplyr::filter(Year==2021) 


```

```{r}
Data2021 %>% 
   group_by(Month_of_Report)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y=Number), color='grey',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2021 number of entries',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  #hc_add_theme(hc_theme_darkunica())%>% 
  hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of entries' )) %>% 
  hc_xAxis(title=list(text='Months'))


```


Row {data-height=400}
-----------------------------------------------------------------------

### Number of entries, Year 2022
```{r}
Data2022<-Data %>% 
   dplyr::filter(Year==2022) 
```

```{r}
Data2022 %>% 
  group_by(Month_of_Report)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y=Number),color='blue',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
     text='2022 number of entries',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  #hc_add_theme(hc_theme_darkunica())%>% 
  hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of entries' )) %>% 
  hc_xAxis(title=list(text='Months'))


```


Row {data-height=400}
-----------------------------------------------------------------------

### Number of entries, Year 2023
```{r}
Data2023<-Data %>% 
   dplyr::filter(Year==2023) 
```

```{r}
Data2023 %>% 
  group_by(Month_of_Report)%>% 
   
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y=Number), color='magenta',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2023 number of entries',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  #hc_add_theme(hc_theme_darkunica())%>% 
  hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of entries' )) %>% 
  hc_xAxis(title=list(text='Months'))

```




# {Monthly number of Doors}
```{r}
  
```


Row {data-height=400}
-----------------------------------------------------------------------

### Number of Doors, Year 2021


```{r}
Data2021 %>% 
  group_by(Month_of_Report)%>% 
  arrange(Month_of_Report)%>%
  summarise(System_Doors=sum(System_Doors))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-System_Doors)%>%# indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y= System_Doors),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2021 Monthly Total Doors',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_bloom())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))

```


Row {data-height=500}
-----------------------------------------------------------------------

### Number of Doors, Year 2022

```{r}
Data2022<-Data %>% 
   dplyr::filter(Year==2022) 
```

```{r}

Data2022 %>% 
  group_by(Month_of_Report)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-System_Doors)%>%# indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y= System_Doors), color='green',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2022 Monthly Total Doors',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_sandsignika())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))

```



Row {data-height=450}
--------------------------------------------------------------------

### Number of Doors Year 2023 
```{r}
Data2023<-Data %>% 
   dplyr::filter(Year==2023) 
```


```{r}
Data2023 %>% 
  group_by(Month_of_Report)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-System_Doors)%>%# indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Month_of_Report, y= System_Doors),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2023 Monthly Total Doors',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_smpl())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))  


   
```




# {System Types and Setting}
```{r}
  
```


Row {data-height=400}
-----------------------------------------------------------------------

### System Types 

```{r}
Data %>% 
  group_by(System_type)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% 
  hchart(
    'bar', hcaes(x=System_type, y=Number),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='System Types',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_economist())%>% 
  hc_yAxis(title=list(text='Percentage of Entries' )) %>% 
  hc_xAxis(title=list(text='Months'))  


```

Row {data-height=500}
-----------------------------------------------------------------------

### System Settings

```{r}
Data %>% 
  group_by(Setting)%>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Setting, y=Number),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nakuru System Settings',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Percentage of the Entries' )) %>% 
  hc_xAxis(title=list(text='Years'))



```




# {Population Served per Year}
```{r}
  
```


Row {data-height=500}
-----------------------------------------------------------------------

### Population Served for the Year 2021

```{r}

Data2021 %>% 
  group_by(Month_of_Report)%>% 
  summarise(Population=sum(System_Users))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-Population)%>%# indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Month_of_Report, y= Population), color='blue',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2021 Population Served',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_bloom())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))


```

Row {data-height=500}
-----------------------------------------------------------------------

### Population Served for the Year 2022

```{r}
Data2022 %>% 
  group_by(Month_of_Report)%>% 
  summarise(Population=sum(System_Users))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-Population)%>%# indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Month_of_Report, y= Population),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2022 Population Served',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_bloom())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))


```

Row {data-height=500}
-----------------------------------------------------------------------

### Population Served for the Year 2023

```{r}
Data2023%>% 
  group_by(Month_of_Report)%>% 
  summarise(Population=sum(System_Users))%>%
  #summarise(System_Users=sum(System_Users)) %>% 
  arrange(-Population)%>%# indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Month_of_Report, y= Population), color='orange',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='2023 Population Served',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_bloom())%>% 
  hc_yAxis(title=list(text='Number of System Doors' )) %>% 
  hc_xAxis(title=list(text='Months'))


```


# {Nawassco Trend}
```{r}
  
```

```{r}
Nawassco<-Data %>% 
   dplyr::filter(Sub_county=='Nakuru Town East'| Sub_county=='Nakuru Town West') 
```


Row {data-height=500}
-----------------------------------------------------------------------

### Nawassco Number of Toilets (Doors)

```{r}

Nawassco %>% 
  group_by(Year)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
 arrange(System_Doors) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=System_Doors), color='blue',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nawassco Number of Systems Doors per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))

```

Row {data-height=500}
-----------------------------------------------------------------------

### Nawassco Population Served

```{r}
Nawassco%>% 
  group_by(Year)%>% 
  summarise(population=sum(System_Users))%>%
 arrange(-population) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=population),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nawassco Number of Population Served per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))


```


Row {data-height=500}
-----------------------------------------------------------------------

### Nawassco System Class 2023

```{r}
Nawassco %>% 
  group_by(System_Class)%>% 
   filter(Year=='2023') %>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=System_Class, y=Number), color='violet',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Nawasco System Class 2023',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number' )) %>% 
  hc_xAxis(title=list(text='System Class'))


```

Row {data-height=500}
-----------------------------------------------------------------------

### Nawassco Data

```{r}
 datatable(Nawasscoshp,
          caption = "Nawassco Constructed and Improved Toilets Under Partnership                      with FnishINK",
          rownames = T,
          filter = "top",
          class = "hover cell-border stripe", #for making grid cells
          #editable = "cell", # for editing cells
          extensions="Buttons",
          options = list(pageLength = 80,dom="Bfrtip", buttons=c( 'copy','csv', '' ))) 

```

# {Naruwasco Trend}
```{r}
  
```

```{r}
Naruwasco<-Data %>% 
   dplyr::filter(Sub_county=='Molo'| Sub_county=='Rongai') 
```


Row {data-height=500}
-----------------------------------------------------------------------

### Naruwasco Number of Toilets (Doors)

```{r}

Naruwasco%>% 
  group_by(Year)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
 #arrange(-System_Doors) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=System_Doors), color='blue',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Naruwasco Number of Systems Doors per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))



```

Row {data-height=500}
-----------------------------------------------------------------------

### Naruwasco Population Served

```{r}
Naruwasco%>% 
  group_by(Year)%>% 
  summarise(population=sum(System_Users))%>%
 arrange(population) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=population),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Naruwasco Number of Population Served per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))


```


Row {data-height=500}
-----------------------------------------------------------------------

### Naruwasco System Class 2023

```{r}
Naruwasco %>% 
  group_by(System_Class)%>% 
   filter(Year=='2023') %>% 
  summarise(Number=n()) %>% 
  arrange(Number) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=System_Class, y=Number), color='violet',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Naruwasco System Class 2023',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  hc_yAxis(title=list(text='Number' )) %>% 
  hc_xAxis(title=list(text='System Class'))


```


Row {data-height=500}
-----------------------------------------------------------------------

### Naruwasco Data

```{r}
 datatable(Naruwasco,
          caption = "Naruwasco Constructed and Improved Toilets Under Partnership              with FnishINK",
          rownames = T,
          filter = "top",
          class = "hover cell-border stripe", #for making grid cells
          #editable = "cell", # for editing cells
          extensions="Buttons",
          options = list(pageLength = 80,dom="Bfrtip", buttons=c( 'copy','csv', '' )))


```


# {Naivawasco Trend}
```{r}
  
```

```{r}
Naivawasco<-Data %>% 
   dplyr::filter(Sub_county== 'Naivasha') 
```


Row {data-height=500}
-----------------------------------------------------------------------

### Naivawasco Number of Toilets (Doors)

```{r}
Naivawasco%>% 
  group_by(Year)%>% 
  summarise(System_Doors=sum(System_Doors))%>%
 arrange(System_Doors) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=System_Doors), color='blue',
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Naivawasco Number of Systems Doors per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))


```

Row {data-height=500}
-----------------------------------------------------------------------

### Naivawasco Population Served
```{r}
Naivawasco%>% 
  group_by(Year)%>% 
  summarise(population=sum(System_Users))%>%
 arrange(population) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Year, y=population), 
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Naivawasco Number of Population Served per Year',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_ffx())%>% 
  #hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number of Doors' )) %>% 
  hc_xAxis(title=list(text='Years'))


```


Row {data-height=500}
-----------------------------------------------------------------------

### Naivawasco System Class 2023

```{r}



```


Row {data-height=500}
-----------------------------------------------------------------------

### Naivawasco Data

```{r}
 datatable(Naivawasco,
          caption = "Naivawasco Constructed and Improved Toilets Under Partnership              with FnishINK",
          rownames = T,
          filter = "top",
          class = "hover cell-border stripe", #for making grid cells
          #editable = "cell", # for editing cells
          extensions="Buttons",
          options = list(pageLength = 80,dom="Bfrtip", buttons=c( 'copy','csv', '' )))


```



# {Data}
```{r}

```




```{r}

 datatable(Datashp,
          caption = "Nakuru Constructed and Improved Toilets Under Partnership              with FnishINK",
          rownames = T,
          filter = "top",
          class = "hover cell-border stripe", #for making grid cells
          #editable = "cell", # for editing cells
          extensions="Buttons",
          options = list(pageLength = 80,dom="Bfrtip", buttons=c( 'copy','csv', '' )))

```

```{r}

```




